Supplementary information

### 2021-09-28 _targets.Rmd
add oforecast plotting

```{r}
library(targets)
library(tibble)
library(tidyr)
library(dplyr)
library(scoringutils)
library(ggplot2)
library(purrr)
library(here)
tar_unscript()
```

@@

```{targets globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
library(purrr)
library(here)
functions <- list.files(here("R"), full.names = TRUE)
walk(functions, source)
tar_option_set(
  packages = c("tibble", "tidyr", "dplyr", "scoringutils", "ggplot2", "purrr")
)
```

@@

- Define a grid of scenarios including the true values (zero growth rate or cumulative linear error).

```{targets toy_scenarios, tar_simple = TRUE}
expand_grid(
  init = c(100),
  r = c(0, 0.01, 0.1, -0.01, -0.1),
  r_error = c(0, 0.01, 0.025, 0.05, 0.1, -0.01, -0.025, -0.05, -0.1),
  additive_error = c(0, 1, 10, -1, -10)
) |> 
  mutate(id = 1:n())
```

@@

```{targets toy_forecasts, tar_simple = TRUE}
toy_simulations |>
  filter(!(r_error == 0 & additive_error == 0)) |>
  select(init, r, r_error, additive_error, time, sample = sim,
         prediction = obs) |>
  left_join(toy_truth, by = c("init", "r", "time"))
```

@@

```{targets plot_toy_scores_by_horizon, tar_simple = TRUE}
toy_scores |>
  filter(time <= 4) |>
  plot_scores_by_horizon()
```

@@

```{targets plot_toy_log_scores_by_horizon, tar_simple = TRUE}
toy_log_scores |>
  filter(time <= 4) |>
  plot_scores_by_horizon()
```

@@

```{targets plot_toy_scores_by_scale, tar_simple = TRUE}
toy_all_scores |>
  filter(time == 4) |>
  plot_scores_by_scale()
```

@@

```{targets save_toy_output}
list(
  tar_target(
    toy_scores_csv, 
    save_csv(toy_all_scores, here("output/data/toy_all_scores.csv")),
    format = "file"
  ),
  tar_target(
    toy_scores_by_scale_file, 
    save_plot(plot_toy_scores_by_scale, 
              here("output", "figures", "toy_scores_by_scale.png"),
    format = "file")
            ),
  tar_target(
    toy_scores_by_horizon_file, 
    save_plot(plot_toy_scores_by_horizon, 
              here("output", "figures", "toy_scores_by_horizon.png"),
    format = "file")
            ),
  tar_target(
    toy_log_scores_by_horizon_file, 
    save_plot(plot_toy_log_scores_by_horizon, 
              here("output", "figures", "toy_log_scores_by_horizon.png"),
    format = "file")
            )
)
```

>>>>

```{r}
library(targets)
library(tarchetypes)
library(tibble)
library(tidyr)
library(dplyr)
library(scoringutils)
library(ggplot2)
library(purrr)
library(here)
tar_unscript()
```

@@

```{targets globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
library(purrr)
library(here)
library(tibble)
library(tarchetypes)
functions <- list.files(here("R"), full.names = TRUE)
walk(functions, source)
tar_option_set(
  packages = c("tibble", "tidyr", "dplyr", "scoringutils", "ggplot2", "purrr",
               "readr"),
  error = "workspace"
)
```

@@

- Define a set of growth rates to explore.

```{targets toy_globals, tar_globals = TRUE}
toy_growth_rates <- tibble(r = c(0, 0.01, 0.1, -0.01, -0.1))
```

- Define a grid of scenarios including the true values (zero growth rate and cumulative linear error) for this set of growth rates.

```{targets toy_scenarios, tar_simple = TRUE}
expand_grid(
  init = c(100),
  r = toy_growth_rates$r,
  r_error = c(0, 0.01, 0.025, 0.05, 0.1, -0.01, -0.025, -0.05, -0.1),
  additive_error = c(0, 1, 10, -1, -10)
) |> 
  mutate(id = 1:n())
```

@@

```{targets toy_forecasts, tar_simple = TRUE}
toy_simulations |>
  select(init, r, r_error, additive_error, time, sample = sim,
         prediction = obs) |>
  left_join(toy_truth, by = c("init", "r", "time"))
```

- Plot simulated observations and forecasts for each growth rate stratified by assumed growth rate and additive error.

```{targets plot_toy_forecasts, tar_interactive = FALSE}
tar_map(
  toy_growth_rates,
  tar_target(
    toy_forecasts_plot,
    plot_toy_forecasts(toy_forecasts, growth = r[[1]],
                       alpha = 0.2, samples = 10)
  ),
  tar_target(
    plot_toy_forecasts_file,
    save_plot(
      toy_forecasts_plot, 
      here("output", "figures", 
           paste0("plot_toy_forecasts_", r[[1]], ".png"))
    ),
    format = "file")
)
```

@@

```{targets toy_scores_by_horizon_plot, tar_simple = TRUE}
toy_scores |>
  filter(time <= 4) |>
  plot_toy_scores_by_horizon()
```

@@

```{targets toy_log_scores_by_horizon_plot, tar_simple = TRUE}
toy_log_scores |>
  filter(time <= 4) |>
  plot_toy_scores_by_horizon()
```

@@

```{targets toy_scores_by_scale_plot, tar_simple = TRUE}
toy_all_scores |>
  filter(time == 4) |>
  plot_toy_scores_by_scale()
```

@@

```{targets save_toy_output}
list(
  tar_target(
    toy_scores_csv, 
    save_csv(toy_all_scores, here("output/data/toy_all_scores.csv")),
    format = "file"
  ),
  tar_target(
    toy_scores_by_scale_file, 
    save_plot(toy_scores_by_scale_plot, 
              here("output", "figures", "toy_scores_by_scale.png"),
    format = "file")
            ),
  tar_target(
    toy_scores_by_horizon_file, 
    save_plot(toy_scores_by_horizon_plot, 
              here("output", "figures", "toy_scores_by_horizon.png"),
    format = "file")
            ),
  tar_target(
    toy_log_scores_by_horizon_file, 
    save_plot(toy_log_scores_by_horizon_plot, 
              here("output", "figures", "toy_log_scores_by_horizon.png"),
    format = "file")
            )
)
```
